Test data

### 2022-07-20 Shiny/Test/Flexdashboard rows.Rmd
read_proff8 function. met.brewer test

    # Creating the value box for administrative expenses
    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "Admin spend",
        color = "primary",
        icon = "fa-random"
        )
      })

>>>>

    # Creating the value box for administrative expenses
    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "Admin spend",
        color = met.brewer("Wissing", n = 1),
        icon = "fa-random"
        )
      })

### 2022-07-20 Shiny/Test/Test data.Rmd
read_proff8 function. met.brewer test

@@

identical(kreft_html, kreft_html3)
```

@@

@@

>>>>

read_proff8 <- function(file, start, end){
    read_html(file, encoding = "UTF-8") |> 
      html_node("#inner-frame") |> 
      html_table() |> 
      select( # removing empty column
        REGNSKAPSPERIODE:all_of(start)) |> # using all_of()
      mutate( # removing whitespace
        REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
      ) |> 
      filter( # removing duplicate table - no idea why it's necessary
        !row_number() > 176
      ) |>
      filter( # removing duplicate rows
        !grepl("Lukk", REGNSKAPSPERIODE)
      ) |> 
      pivot_longer( # tidying data
        all_of(end):all_of(start), names_to = "year"
        ) |> # using all_of()
      mutate( # changing to real NAs and turning years into numbers
        value = na_if(value, "-"),
        year = as.integer(year), 
        valutakode = ifelse(REGNSKAPSPERIODE == "Valutakode", value, NA)
      ) |> 
      fill( # filling the currency column
        valutakode, .direction = "updown"
      ) |> 
      filter( # removing dates and redundant currency
        REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
          REGNSKAPSPERIODE != "Valutakode") |> 
      mutate( # removing whitespace in numbers
        value = str_replace_all(value, "\\s", ""),
        value = as.numeric(value),
        value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value),
        value = value * 1000
      ) |> 
      distinct() |> # removing any remaining duplicate rows
      pivot_wider( # pivoting
        names_from = REGNSKAPSPERIODE, values_from = value
      ) |> 
      clean_names() |> # tidying names
      select(-lederlonn_i_hele_1000,
             -resultatregnskap_i_hele_1000,
             -balanseregnskap_i_hele_1000) |> # removing headings
      rename( # making it clear what lonn refers to
        lederlonn = lonn
      ) |> 
      arrange(desc(year)) # arranging by year
}

@@

identical(kreft_html, kreft_html3)

kreft_html5 <- read_proff8("Data/Kreftforeningen.html", "2002", "2021")

identical(kreft_html, kreft_html5)
```

@@

annual_profit
balance_positive

@@

```{r}
